---
title: "Homework 6"
author: "Sam Brewer"
date: "2/23/2022"
output: html_document
---

## Open Libraries
```{r}
library(ggplot2) # for graphics
library(MASS) # for maximum likelihood estimation
```

## My Own Data
```{r}
z <- read.table("Cleaned2021VegetationData.csv",header=TRUE,sep=",")
str(z)
summary(z)
```

## Read in Data Vector
```{r}
# quick and dirty, a truncated normal distribution to work on the solution set

#z <- rnorm(n=3000,mean=0.2)
#z <- data.frame(1:3000,z)
#names(z) <- list("ID","myVar")
#z <- z[z$myVar>0,]
#str(z)
#summary(z$myVar)
```


## Plot Histogram of Data
```{r}
p1 <- ggplot(data=z, aes(x=Height_cm, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

## Add Emperical Density Curve
```{r}
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```

## Get Maximum Likelihood Parameters for Normal
```{r}
normPars <- fitdistr(z$Height_cm,"normal")
print(normPars)
str(normPars)
normPars$estimate["mean"] # note structure of getting a named attribute
```

## Plot `Normal` Probability Density
```{r}
meanML <- normPars$estimate["mean"]
sdML <- normPars$estimate["sd"]
xval <- seq(0,max(z$Height_cm),len=length(z$Height_cm))
stat <- stat_function(aes(x = xval, y = ..y..), fun = dnorm, colour="red", n = length(z$Height_cm), args = list(mean = meanML, sd = sdML))
p1 + stat
```

## Plot `Exponential` Probability Density
```{r}
expoPars <- fitdistr(z$Height_cm,"exponential")
rateML <- expoPars$estimate["rate"]
stat2 <- stat_function(aes(x = xval, y = ..y..), fun = dexp, colour="blue", n = length(z$Height_cm), args = list(rate=rateML))
p1 + stat + stat2
```

## Plot `Uniform` Probability Density
```{r}
stat3 <- stat_function(aes(x = xval, y = ..y..), fun = dunif, colour="darkgreen", n = length(z$Height_cm), args = list(min=min(z$myVar), max=max(z$myVar)))
p1 + stat + stat2 + stat3
```

## Plot `Gamma` Probability Density
```{r}
gammaPars <- fitdistr(z$Height_cm,"gamma")
shapeML <- gammaPars$estimate["shape"]
rateML <- gammaPars$estimate["rate"]
stat4 <- stat_function(aes(x = xval, y = ..y..), fun = dgamma, colour="brown", n = length(z$Height_cm), args = list(shape=shapeML, rate=rateML))
p1 + stat + stat2 + stat3 + stat4
```

## Plot `Beta` Probability Density
```{r}
pSpecial <- ggplot(data=z, aes(x=Height_cm/(max(Height_cm + 0.1)), y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) + 
  xlim(c(0,1)) +
  geom_density(size=0.75,linetype="dotted")

betaPars <- fitdistr(x=z$Height_cm/max(z$Height_cm + 0.1),start=list(shape1=1,shape2=2),"beta")
shape1ML <- betaPars$estimate["shape1"]
shape2ML <- betaPars$estimate["shape2"]
statSpecial <- stat_function(aes(x = xval, y = ..y..), fun = dbeta, colour="orchid", n = length(z$Height_cm), args = list(shape1=shape1ML,shape2=shape2ML))
pSpecial + statSpecial
```

**Gamma is the best fitting distribution.**

## Simulate New Data Set
```{r}
#generate data using gamma
z <- rgamma(n=288,
            shape=3.568224649,
            rate=0.101954357)
z <- data.frame(1:288,z)
names(z) <- list("ID","Height_cm")
z <- z[z$Height_cm>0,]
str(z)
summary(z$Height_cm)
#plot histogram
p1 <- ggplot(data=z, aes(x=Height_cm, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
#add probability density curve
p1 <-  p1 +  geom_density(linetype="dotted",size=0.75)
print(p1)
```
## Histogram of Original Data
```{r}
z <- read.table("Cleaned2021VegetationData.csv",header=TRUE,sep=",")
p1 <- ggplot(data=z, aes(x=Height_cm, y=..density..)) +
  geom_histogram(color="grey60",fill="cornsilk",size=0.2) 
print(p1)
```

## **Questions**

How do the two histogram profiles compare? Do you think the model is doing a good job of simulating realistic data that match your original measurements? Why or why not?

The actual data has more of a bimodal distribution so it deviates from the simulated one which is unimodal skewed right, but for the left hand side of the plot it is similar.

