---
title: "Homework_08"
author: "Sam Brewer"
date: "3/16/2022"
output: html_document
---
# Homework 8

[Study used](https://www.epa.gov/sites/default/files/2016-06/documents/phosphorus-tmdls-vermont-segments-lake-champlain-jun-17-2016.pdf)

The long-term response of phosphorus concentrations is modeled by the equation `Y = 53.74 – 47.04 X` for the Missisquoi Bay where Y = predicted bay annual average total phosphorus concentration (µg/L) 70 years after watershed load
reduction is achieved
X = percent (as decimal fraction) watershed phosphorus load reduction from base period rates

## Creating the simulated data for 50% phosphorus loading capacity
```{r}
beta1 <- 53.74 # slope
beta0 <- 47.04 # intercept
noise <- rnorm(n=100, mean=0, sd=0.05) # adds variation to the data set
x_normalP <- rnorm(n=100, mean=0.50, sd=0.050)
y_normalP <- beta0 + beta1*x_normalP +noise
head(x_normalP)
head(y_normalP)
```
## Other data sets for 75%, 25%, and 50% with low SD, respectively

```{r}
x_highP <- rnorm(n=100, mean=0.75, sd=0.050)
y_highP <- beta0 + beta1*x_highP + noise
head(x_highP)
head(y_highP)

x_lowP <- rnorm(n=100, mean=0.25, sd=0.050)
y_lowP <- beta0 + beta1*x_lowP + noise
head(x_lowP)
head(y_lowP)

x_lowsdP <- rnorm(n=100, mean=0.50, sd=0.005)
y_lowsdP <- beta0 + beta1*x_lowsdP + noise
head(x_lowsdP)
head(y_lowsdP)
```

## Creating a data frame
```{r}
d_frame <- data.frame(x_normalP,y_normalP,x_highP,y_highP,x_lowP,y_lowP,x_lowsdP,y_lowsdP)
```

## Data Analysis with Linear Regression of 50% P

```{r}
library(ggplot2)

reg_model <- lm(y_normalP~x_normalP,data=d_frame)

slope <- summary(reg_model)$coefficients[1,1]
intercept <- summary(reg_model)$coefficients[1,2]
slope == beta0
intercept == beta1

reg_plot <- ggplot(data=d_frame, aes(x=x_normalP, y=y_normalP)) +
            geom_point() +
            stat_smooth(method=lm,se=0.95)
print(reg_plot)
  
```

## Different Means

### 75% P
```{r}
reg_model <- lm(y_highP~x_highP,data=d_frame)

slope <- summary(reg_model)$coefficients[1,1]
intercept <- summary(reg_model)$coefficients[1,2]
slope == beta0
intercept == beta1

reg_plot <- ggplot(data=d_frame, aes(x=x_highP, y=y_highP)) +
            geom_point() +
            stat_smooth(method=lm,se=0.95)
print(reg_plot)
```

### 25% P
```{r}
reg_model <- lm(y_lowP~x_lowP,data=d_frame)

slope <- summary(reg_model)$coefficients[1,1]
intercept <- summary(reg_model)$coefficients[1,2]
slope == beta0
intercept == beta1

reg_plot <- ggplot(data=d_frame, aes(x=x_lowP, y=y_lowP)) +
            geom_point() +
            stat_smooth(method=lm,se=0.95)
print(reg_plot)
```

## Different Standard Deviation

### low SD, 50% P
```{r}
reg_model <- lm(y_lowsdP~x_lowsdP,data=d_frame)

slope <- summary(reg_model)$coefficients[1,1]
intercept <- summary(reg_model)$coefficients[1,2]
slope == beta0
intercept == beta1

reg_plot <- ggplot(data=d_frame, aes(x=x_lowsdP, y=y_lowsdP)) +
            geom_point() +
            stat_smooth(method=lm,se=0.95)
print(reg_plot)
```

## Different Sample Size

### n=10
```{r}
x_small <- rnorm(n=10, mean=0.50, sd=0.050)
y_small <- beta0 + beta1*x_small + noise
head(x_small)
head(y_small)

d_frame <- data.frame(x_small,y_small)

reg_model <- lm(y_small~x_small,data=d_frame)

slope <- summary(reg_model)$coefficients[1,1]
intercept <- summary(reg_model)$coefficients[1,2]
slope == beta0
slope
intercept == beta1

reg_plot <- ggplot(data=d_frame, aes(x=x_small, y=y_small)) +
            geom_point() +
            stat_smooth(method=lm,se=0.95)
print(reg_plot)
```
The slope is still very close to the original at this small sample size. I added noise for all simulations above to try and make the regression less close to the original equation.



